Evaluating infectious disease forecasts with allocation scoring rules

### 2023-11-07 alloscore_manuscript/alloscore-application.Rnw
Update alloscore-application.Rnw
CRPS/WIS comment

The weighted interval score (WIS) was proposed in 2020 as a way to score forecasts that were being made in the early stages of the COVID-19 pandemic \citep{bracher2021evaluating}; equivalent scores had also been used in previous forecast evaluation efforts \cite[e.g.,][]{hong2016probabilisticEnergyForecasting}.
The WIS is a proper scoring rule for forecasts that use a set of quantiles to represent a probabilistic forecast distribution.
%% optional detail
Many early COVID-19 modeling efforts, including the US COVID-19 Forecast Hub and other collaborative forecasting projects, adopted a quantile forecast format as a matter of convenience (e.g., this format does not require the forecaster to pre-specify an upper bound for disease counts as would be required to collect forecasts in the format of bin probabilities) \citep{cramer_united_2022}.
%%
While pointing a reader interested in more mathematical detail to \cite{bracher2021evaluating}, we note simply that the WIS is a weighted sum of interval scores at different probability levels (e.g., 50\% prediction intervals, 80\% PIs, 95\% PIs, etc...).
Larger interval scores indicate less skillful forecasts.
An interval score consists of (a) the width of the interval, with larger intervals receiving higher scores, and (b) a penalty if the interval does not cover the eventual observation, which increases the further away the interval is from the observed value.
Equivalently, the WIS can also be characterized as a weighted sum of quantile scores for each individual predictive quantile.
The quantile score for a particular quantile level assigns an asymmetric penalty to predictions that are too high or too low, with the relative sizes of the penalties set so that in expectation the score is minimized by the given quantile of the distribution.
The most commonly used version of WIS is one that uses an equal weighting of all quantile levels, in which case WIS approximates the continuous rank probability score (CRPS), a commonly used score for probabilistic forecasts.
\emph{It is important to note that this weighting was proposed because the resulting score approximates the CRPS, and not because it aligned with any particular public health decision-making rationale.}

>>>>

The weighted interval score (WIS) was proposed in 2020 as a way to score forecasts that were being made in the early stages of the COVID-19 pandemic \citep{bracher2021evaluating}; equivalent scores had also been used in previous forecast evaluation efforts \cite[e.g.,][]{hong2016probabilisticEnergyForecasting}.
The WIS is a proper scoring rule for forecasts that use a set of quantiles to represent a probabilistic forecast distribution.
%% optional detail
Many early COVID-19 modeling efforts, including the US COVID-19 Forecast Hub and other collaborative forecasting projects, adopted a quantile forecast format as a matter of convenience (e.g., this format does not require the forecaster to pre-specify an upper bound for disease counts as would be required to collect forecasts in the format of bin probabilities) \citep{cramer_united_2022}.
%%
While pointing a reader interested in more mathematical detail to \cite{bracher2021evaluating}, we note simply that the WIS is a weighted sum of interval scores at different probability levels (e.g., 50\% prediction intervals, 80\% PIs, 95\% PIs, etc...).
Larger interval scores indicate less skillful forecasts.
An interval score consists of (a) the width of the interval, with larger intervals receiving higher scores, and (b) a penalty if the interval does not cover the eventual observation, which increases the further away the interval is from the observed value.
Equivalently, the WIS can also be characterized as a weighted sum of quantile scores for each individual predictive quantile.
The quantile score for a particular quantile level assigns an asymmetric penalty to predictions that are too high or too low, with the relative sizes of the penalties set so that in expectation the score is minimized by the given quantile of the distribution.
The most commonly used version of WIS is one that uses an equal weighting of all quantile levels, in which case WIS approximates the continuous ranked probability score (CRPS), a commonly used score for probabilistic forecasts.
\apg{Maybe a rewording and/or a supplement reference here to mention that any WIS approximates the a corresponding weighted CRPS, and that WIS actually is the wCRPS for a discrete measure/weighting.}
\emph{It is important to note that this weighting was proposed because the resulting score approximates the CRPS, and not because it aligned with any particular public health decision-making rationale.}
